Two sample $t$ test example using `nycflights13` `flights` data

### 2018-03-30 inst/doc/chisq_test.Rmd
Tweak pkgdown

```{r }
fli_small %>%
  specify(origin ~ season) %>% # alt: response = origin, explanatory = season
  hypothesize(null = "independence") %>%
  # calculate(stat = "Chisq") ## Not needed since Chisq is implied based on variable types
  visualize(method = "theoretical", obs_stat = obs_chisq, direction = "right")
```

>>>>

```{r }
fli_small %>%
  specify(origin ~ season) %>% # alt: response = origin, explanatory = season
  hypothesize(null = "independence") %>%
  # calculate(stat = "Chisq") ## Not needed since Chisq is implied
  visualize(method = "theoretical", obs_stat = obs_chisq, direction = "right")
```

### 2018-03-30 inst/doc/profiles_examples_both_methods.Rmd
Tweak pkgdown

```{r}
prof_small %>%
  specify(drugs ~ status) %>% # alt: response = drugs, explanatory = status
  hypothesize(null = "independence") %>%
  # generate() is not needed since we are not doing randomization
  # calculate(stat = "Chisq") ## Not needed since Chisq implied based on variable types
  visualize(method = "theoretical")
```

@@

```{r}
prof_small %>%
  specify(drugs ~ NULL) %>% # alt: response = drugs
  hypothesize(null = "point", 
              p = c("never" = .7, "often" = .05, "sometimes" = .25)) %>%
  # generate() is not needed since we are not doing randomization
  # calculate(stat = "Chisq") ## Not needed since z implied based on variable types
  visualize(method = "theoretical")
```

@@

```{r}
prof_small %>%
  specify(age ~ height) %>% # alt: response = age, explanatory = height
  hypothesize(null = "independence") %>%
  # generate() is not needed since we are not doing randomization
  # calculate(stat = "t") ## Not needed since z implied based on variable types
  visualize(method = "theoretical")
```

>>>>

```{r}
prof_small %>%
  specify(drugs ~ status) %>% # alt: response = drugs, explanatory = status
  hypothesize(null = "independence") %>%
  # generate() is not needed since we are not doing randomization
  # calculate(stat = "Chisq") ## Not needed since Chisq implied
  visualize(method = "theoretical")
```

@@

```{r}
prof_small %>%
  specify(drugs ~ NULL) %>% # alt: response = drugs
  hypothesize(null = "point", 
              p = c("never" = .7, "often" = .05, "sometimes" = .25)) %>%
  # generate() is not needed since we are not doing randomization
  # calculate(stat = "Chisq") ## Not needed since Chisq implied
  visualize(method = "theoretical")
```

@@

```{r}
prof_small %>%
  specify(age ~ height) %>% # alt: response = age, explanatory = height
  hypothesize(null = "independence") %>%
  # generate() is not needed since we are not doing randomization
  # calculate(stat = "t") ## Not needed since t implied based on variable types
  visualize(method = "theoretical")
```

### 2018-03-30 inst/doc/two_sample_t.Rmd
Tweak pkgdown

```{r}
t_null_distn <- fli_small %>%
  specify(arr_delay ~ half_year) %>% # alt: response = arr_delay, explanatory = half_year
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "t")
t_null_distn %>% visualize(obs_stat = obs_t, direction = "two_sided")
```

@@

```{r }
fli_small %>%
  specify(arr_delay ~ half_year) %>% # alt: response = arr_delay, explanatory = half_year
  hypothesize(null = "independence") %>%
  # calculate(stat = "t") ## Not needed since t is implied based on variable types
  visualize(method = "theoretical", obs_stat = obs_t, direction = "two_sided")
```

@@

```{r eval=FALSE}
fli_small %>%
  specify(arr_delay ~ half_year) %>% # alt: response = arr_delay, explanatory = half_year
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "t") %>% 
  visualize(method = "both", obs_stat = obs_t, direction = "two_sided")
```

>>>>

```{r}
t_null_distn <- fli_small %>%
  # alt: response = arr_delay, explanatory = half_year
  specify(arr_delay ~ half_year) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "t", order = c("h1", "h2"))
t_null_distn %>% visualize(obs_stat = obs_t, direction = "two_sided")
```

@@

```{r }
fli_small %>%
  # alt: response = arr_delay, explanatory = half_year
  specify(arr_delay ~ half_year) %>%
  hypothesize(null = "independence") %>%
  # calculate(stat = "t") ## Not needed since t is implied
  visualize(method = "theoretical", obs_stat = obs_t, direction = "two_sided")
```

@@

```{r eval=FALSE}
fli_small %>%
  # alt: response = arr_delay, explanatory = half_year
  specify(arr_delay ~ half_year) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "t", order = c("h1", "h2")) %>% 
  visualize(method = "both", obs_stat = obs_t, direction = "two_sided")
```
